A comparison on R tools for nonlinear least squares modeling

### 2023-03-13 RefactoringNLS/ComparingNLStools.Rmd
update bib and smaller pkgs

The tools we will compare are the base-R `nls()` function 
and a number of packages that are available on the CRAN repository.
Of these, we will pay particular attention to **nlsr** (@nlsr2023manual),
**minpack.lm** (@minpacklm12), 
gslnls (@gslnls23), and nls2 (@nls2-22).

@@

onls -- when there are errors in variables, this minimizes the orthogonal 
residuals

>>>>

The tools we will consider are the base-R `nls()` function 
and a number of packages that are available on the CRAN repository.
Of these, we will pay particular attention to **nlsr** (@nlsr2023manual),
**minpack.lm** (@minpacklm12), 
gslnls (@gslnls23), and nls2 (@nls2-22).

@@

onls (@R-onls-manual) -- when there are errors in variables, this minimizes the orthogonal 
residuals
